% INFORMATION
\def\projectinfoleft{
  Author:\\
  Studnet ID: \\
  First Supervisor: \\
  Second Superviser:
}
\def\projectinforight{
  Haoxuan Wang \\
  201219597 \\
  Dr. Othon Michail \\
  Dr. Vitaliy Kurlin
}
\def\reporttitle{
 COMP 395 Internet Computing Final Year Project : \\

 Simulation, Visualization and Experimental analysis for \\Population Protocols and Network Constructor
\\ in 2-Dimensional Case}
\def\studentid{
  Studnet ID: 201219597 \\
}
\def\department{
Department of Computer Science\\ University of Liverpool
}
\def\theabstract{ %
\large{
\noindent
Population protocol is a theoretical model for distributed computation \cite{AspnesR2007, MCS11}.
The model contains a collection of indistinguishable agents. The network constructor \cite{MS16a} and the
terminating grid network constructor \cite{Mi17} are two models extending population protocol and are able to construct network in different topologies.
\newline

\par\noindent
The main aims of this project is to study for these three distributed theoretical models and then experimentally simulate and visualise protocols
via building the simulator and visualizer. In order to effectively simulate the models of terminating grid network constructor,
the author studies and list all possible kinds of situation for illegal configurations (which are vectors describing the status for
agents) and presents solutions to avoid these illegal cases happens. The simulator was finally built up using
Kotlin language and some related libraries. During the period for implementation of model in the software , the test-driven method was
applied and the unit tests had been written before any model related coding started. To ensure the extensibility of the
simulator, the reflection technique was used to dynamically load user defined protocol during
starting period of the application.
\newline

\par\noindent Finally, the simulation experiments for dancing protocol \cite{AspnesR2007} successfully show its inefficiency under
some particular initial configurations. This also demonstrates the simulator is able to assist researches related
to population protocol.
}

}

\def\theacknowledgement{
\centering
\Large{\noindent
\textit{First of all,
I would express my sincere gratitude to my parents, \\
named \textbf{Baoqin Zhou} and \textbf{Yongge Wang}, \\
who enable me have a such a great opportunity to study in a different country
to hone my skills and gain useful knowledge.}
\newline

\par\noindent
\textit{Then I would appreciate \\
\textbf{Dr.Othon Michail}, \textbf{Dr. Vitaliy Kurlin} \\
and many professors, lecturers and teaching assistants \\
in University of Liverpool and Xi'an Jiaotong-Liverpool University, \\
for their outstanding delivery of knowledge and great patience.}
\newline

\par\noindent
\textit{Finally, I would to thanks to my girlfriend,\\
who was never appeared in my past 22 years' life, \\
so I can devote myself in academics. \\
I do expect your appearance though.}}
}

% INFORMATION END

\input{res/header}
\input{res/style}

\begin{document}
\input{res/titlepage}
% Your things
\input{context/introduction}
\input{context/background}
\input{context/data_required}
\input{context/design}
\input{context/realisation}
\input{context/learningpoints}
\input{context/professionalissues}
\clearpage
\makereference{reference.bib}
\clearpage
\appendix
\input{context/appendix}
\end{document}
