\section{Professional issues}
The section will discuss how the project related to \textit{codes of conduct} \cite{bcsconduct} and \textit{codes of practice} \cite{bcspractic} issued by the British Computer Society (BCS).

\subsection{BCS codes of conduct \cite{bcsconduct}}
\paragraph{1. Public Interest}
The related software library \cite{Kotlin,Koma,GraphStream,JUnit} used is either licenced under Apache 2.0, or LGPLv3 or EPL 1.0, which all allow the
reference their software as the library in the code and these licenses are reasonably compatible with each other under the situation that the simulator only use them as a library and does not involve any modifications on them.
Any documents used in the document and in the associated application are well referenced. As clause \textbf{b} stated, "it have due regard for legitimate rights of third parties"\cite{bcsconduct}.

\par\noindent
There is no discrimination on any kind of basis during the entire process of development as the clause \textbf{c} stated.

\par\noindent
 The project had already opened its source code in https://github.com/billweasley/NetworkSimulator, so it could be considered as "promote equal access
 to benefits of IT as clause \textbf{d} stated".

\paragraph{2. Professional Competence and Integrity}
The entire document (this document) and software faithfully reflect my competence of understanding, which
follows what the clause \textbf{a, b} stated.

\paragraph{3. Duty to Relevant Authority}
The document and the entire project process is carefully in accordance with University of
Liverpool. There is no conflict of interest between the author and the University, which complies
with what the clause \textbf{a, b} stated.

\paragraph{4. Duty to Profession}
As mentioned before, the project would share its code online under LGPLv3 license and open to improvements, which by all means is
"encourage and support fellow members in their professional development" as clause \textbf{f} stated.

\subsection{BCS codes of practice \cite{bcspractic}}
\paragraph{When Defining a New Project and Planning}
The requirement document of the project "explained fully the deliverables"  and "ensures
the scope, deliverables, timescales, costs and responsibilities are agreed in advance" \cite{bcspractic}.
\par\noindent
A previous example "NETCS" \cite{DBLP:journals/corr/AmaxilatisLMS15} was found by the author and the author was inspired by its implementation.

\paragraph{When Tracking Progress}
The project was tracked using git commit history and it did not hide any overruns.

\paragraph{When Closing a Project}
As indicated in \cite{bcspractic}, the project summarise the mistakes made, good fortune encountered in \textit{Evaluation} section and
lessons learned in \textit{Learning points} section.
It also discussed further improvements that may benefits to this or other projects as suggested.
